---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dynamicpack

<!-- badges: start -->
<!-- badges: end -->

This package was built to facilitate the analysis of individual differences in the temporal sequence of psychological states. 
So far it consists only of the resample function (more to come!). This function destroys any signal that may be encoded in the temporal sequence of the observations and thus creates a reference frame for the empirical data. Specifically, the function randomly changes the order of the observations for each participant separately for each variable of interest. It does so to ensure that in the resampled data, there are no relationships between these variables anymore due to the order of the observations (i.e., temporal dependencies).  

Although specifically developed for time series data, the function can be applied to any hierarchical data where the aim is to destroy the signal that is encoded in the order of the observations. 

## Installation

dynamicpack is not yet on CRAN. But you can download it from this repository using the devtools package as outlined below. 

``` r
# install.packages("devtools")
devtools::install_github("anabelbue/dynamicpack")
```
## Example

This basic example demonstrates the resample-function. To use the function, simply specify your data, a grouping variable (e.g., IDs of the participants), and the variables for which you want to change the order. 

```{r example}
library(dynamicpack)

dat <- data.frame(participant=rep(1:10, each=10),              #grouping variable 
                  happiness = rnorm(100, mean = 3.5, sd=1.7),  #order should not be changed 
                  stress = rnorm(100, mean = 2, sd= 1.3),      #order should be changed
                  anxiety = rnorm(100, mean = 1.7, sd= 2))     #order should be changed
resampled_dat <- resample(dat, participant, c("stress", "anxiety"))

head(dat) == head(resampled_dat)
 
 
```
